\documentclass[11pt,a4paper,sans]{moderncv}        
\moderncvstyle{classic}                            
\moderncvcolor{blue}                              
\usepackage[left=2.3cm, right=2.8cm, top=1.4cm, bottom=1.3cm]{geometry}
\setlength{\footskip}{136.00005pt}                
\ifxetexorluatex
  \usepackage{fontspec}
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX}
  \setmainfont{Latin Modern Roman}
  \setsansfont{Latin Modern Sans}
  \setmonofont{Latin Modern Mono}
  \setmathfont{Latin Modern Math} 
\else
  \usepackage[T1]{fontenc}
  \usepackage{lmodern}
\fi


\usepackage[english]{babel} 


\name{Farzaneh}{Koohestani}
\title{Master Student, Researcher \\ \& Data Scientist}                               % optional, remove / comment the line if not wanted
\social[linkedin]{farzanehkoohestani}                        % optional, remove / comment the line if not wanted
\social[github]{farkoo}    
\email{farzanehkoohestani2000@gmail.com}                               % optional, remove / comment the line if not wanted                          % optional, remove / 
%\vspace{-1cm}
\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}

\begin{document}

\makecvtitle

\section{Education}

\cventry{2022--Present}{Master's Degree - Artificial Intelligence and Robotics}{Isfahan University of Technology}{Isfahan}{\textit{GPA: 4/4}}{MSc. Thesis: Improving the quality of low-light images using methods based on deep learning}  % arguments 3 to 6 can be left empty
\cvitem{}{Under the supervision of \textit{Dr. Nader karimi and Dr. Shadrokh Samavi}}

\cventry{2018--2022}{Bachelor's Degree - Intelligent systems}{Isfahan University of Technology}{Isfahan}{\textit{GPA: 3.9/4}}{BSc. Project: Investigated a method based on Meta-Learning to recommend appropriate algorithms for classification problems}  % arguments 3 to 6 can be left empty
\cvitem{}{Under the supervision of \textit{Dr. Nader karimi and Dr. Shadrokh Samavi}}



\section{Reseach Papers}
\cventry{2024}{Revealing Shadows: Low-Light Image Enhancement Using Self-Calibrated Illumination}{Accepted in the 2024 32nd International Conference on Electrical Engineering (ICEE)}{}{}{}
\cvitem{}{\textit{\textbf{Farzaneh Koohestani}, Nader Karimi and Shadrokh Samavi}}

\cventry{2024}{Preserving Details in Darkness: A VQ-VAE Based Approach with SSIM Loss for Low-Light Image Enhancement}{Accepted in 2024 IEEE 5th Annual World AI IoT Congress (AIIoT)
}{}{}{}
\cvitem{}{\textit{\textbf{Farzaneh Koohestani}, Zahra Nabizadeh, Nader Karimi and Shadrokh Samavi}}

\cventry{2024}{BrightVAE: Luminosity Enhancement in Underexposed Endoscopic Images}{Under Review}{Biomedical Signal Processing and Control}{}{}
\cvitem{}{\textit{\textbf{Farzaneh Koohestani}, Zahra Nabizadeh, Nader Karimi, Shahram Shirani and Shadrokh Samavi}}

\cventry{2024}{Adaptive Bitrate Selection for Medical Video Compression: Balancing Bandwidth Efficiency and Segmentation Quality}{Under Review}{EMBC}{}{}
\cvitem{}{\textit{\textbf{Farzaneh Koohestani}, Zahra Nabizadeh, Nader Karimi, Shahram Shirani and Shadrokh Samavi}}

\section*{Technical Skills}

\noindent
\begin{tabular}{>{\bfseries}l@{: }p{10cm}}
Programming Languages & Python, C/C++/C\#, Matlab, Verilog, Java \\
AI Related Libraries & TensorFlow, Keras, Pytorch, Scikit-Learn, Numpy, Pandas, Matplotlib, Seaborn, Scipy \\
Image Processing Libraries & OpenCV, PIL \\
Operating Systems & Linux (Ubuntu, CentOS, Arch, Manjaro), Windows\\
Database Management & SQL, MySQL, PostgreSQL\\
\end{tabular}


\section{Research Experience}

\cventry{2022--Present}{Junior Researcher}{HaDIP Laboratory}{Isfahan University of Technology}{}{
{\begin{itemize}
    \item Collaboratively enhanced general and medical images
    \item Worked with CNN, GAN, VAE, and RNN models
%    \item Utilized image-to-image translation models
    \item Generated synthetic images using VQVAE and GAN models in collaboration with peers
    \item Explored quality assessment methods in depth
\end{itemize}}}

\cventry{2021--2022}{Senior Researcher}{HaDIP Laboratory}{Isfahan University of Technology}{}{
{\begin{itemize}
    \item Experienced in Meta-Learning and Image Dataset Analysis for Image Dataset Classification
    \item Utilized Complexity, Clustering, and Network measures to enhance dataset analysis
    \item Investigated diverse image feature extraction methods like AutoEncoders and CNNs
    \item Conducted a comprehensive review of CNN models such as VGG, ResNet, and InceptionNet
%    \item Conducted extensive analysis of ML models such as SVM, RF, and GBM
\end{itemize}}}



\section{Teaching Experience}
\subsection{Teaching Assistance and Coordinator}

\cventry{2020--2022}{Digital System Design I}{Dr. Nader Karimi}{IUT}{}{
{\begin{itemize}%
\item Spring 2022 \& Fall 2022 \& Fall 2021 \& Spring 2020.
%\item Sep 2021 - Feb 2022
%\item Sep 2020 - Feb 2021
%\item Feb 2020 - Jul 2020
\end{itemize}}}

\cventry{2022 \& 2025}{Computational Intelligence}{Dr. Mehran Safayani and Dr. Samaneh Hesseini}{IUT}{}{
\begin{itemize}%
\item Fall 2022 \& Spring 2025.
\end{itemize}}

\cventry{2022}{FPGA}{Dr. Amir Khorsandi}{IUT}{}{
\begin{itemize}%
\item Fall 2022.
\end{itemize}}

\cventry{2022}{Microprocessor}{Dr. Farzaneh Shayegh}{IUT}{}{
\begin{itemize}%
\item Spring 2022.
\end{itemize}}

\cventry{2020--2021}{Advanced Programming (C\#)}{Dr. Mohammadali Khosravifar}{IUT}{}{%
\begin{itemize}%
\item Spring 2021 \& Fall 2020.
%\item Sep 2020 - Feb 2021
\end{itemize}}

\cventry{2019--2021}{Basic Programming}{Dr. Elham Mahmoudzadeh and Dr. Samaneh Hosseini}{IUT}{}{
%
\begin{itemize}%
\item Fall 2020 \&  Fall 2019.
\end{itemize}}

\cventry{2025}{Data Minning}{Dr. Hamidreza Hakim}{IUT}{}{
%
\begin{itemize}%
\item Spring 2025.
\end{itemize}}

\section{Selective Academic Projects}

\cventry{\href{https://github.com/farkoo/GNN-Citations}{\textcolor{blue}{(code)}}}{\textnormal{Investigated the citation network of articles using Graph Neural Networks}}{}{}{}{}

\cventry{\href{https://github.com/farkoo/PG-PPO-OthelloSolver}{\textcolor{blue}{(code)}}}{\textnormal{Othello game-playing agents trained using reinforcement learning techniques}}{}{}{}{}

\cventry{\href{https://github.com/farkoo/Obstacle-Avoiding-Robot}{\textcolor{blue}{(code)}}}{\textnormal{Implementation and construction of an obstacle-avoiding robot using Webots}}{}{}{}{}

\cventry{\href{https://github.com/farkoo/Parkinsons-Diagnosis-ML}{\textcolor{blue}{(code)}}}{\textnormal{Prediction and diagnosis of Parkinson's disease using audio signals}}{}{}{}{}

%\cventry{\href{https://github.com/farkoo/Mask-Detection-ptL}{\textcolor{blue}{(code)}}}{\textnormal{MaskGuard: Image-Based Mask Detection}}{}{}{}{}

\cventry{\href{https://github.com/farkoo/Novel-Seam-Carving-Method}{\textcolor{blue}{(code)}}}{\textnormal{Presenting a new method for seam carving using energy, depth and edge map}}{}{}{}{}

\cventry{\href{https://github.com/farkoo/Covid19-Detection-from-ChestXRayImages}{\textcolor{blue}{(code)}}}{\textnormal{Diagnosis of covid-19 from chest x-ray images}}{}{}{}{}

\cventry{\href{https://github.com/farkoo/Retinal-Vessel-Segmentation}{\textcolor{blue}{(code)}}}{\textnormal{Retinal vessel segmentation using DRIVE dataset}}{}{}{}{}

\cventry{\href{https://github.com/farkoo/Cells-Segmentation-and-Count}{\textcolor{blue}{(code)}}}{\textnormal{Blood cells segmentation and count using image processing techniques}}{}{}{}{}

%\cventry{\href{https://github.com/farkoo/Stock-Market-Detection}{\textcolor{blue}{(code)}}}{\textnormal{Google stock value prediction using Recurrent Neural Network}}{}{}{}{}

\section{Honors}
\cventry{2024}{Ranked  among all Artificial Intelligence students in Master's Degree}{}{}{ }{}
\cventry{2022}{Ranked among all graduated Computer Engineering students in Bachelor's Degree (Intelligent systems)}{}{}{ }{
\begin{itemize}
    \item Directly admitted to MSc. program for outstanding performance as a BSc. student
    \item Membership in Brilliant Talents Foundation and Exceptional Students
    \end{itemize}
} 

\cventry{2018}{Ranked 443 among more than 150,000 participants in the National University's Entrance Exam "Konkur" (Mathematics and Physics)}{}{}{}{}  



\section{References}
\cventry{}{Dr. Shadrokh Samavi}{Professor at Isfahan University of Technology \& Adjunct Professor at McMaster University}{}{}{samavi@mcmaster.ca}  % arguments 3 to 6 can be left empty
\cventry{}{Dr. Nader Karimi}{Associate Professor at Isfahan University of Technology}{}{}{nader.karimi@cc.iut.ac.ir}  % arguments 3 to 6 can be left empty
%\cventry{}{Dr. Mehran Safayani}{Associate Professor at Isfahan University of Technology}{}{}{safayani@iut.ac.ir}  % arguments 3 to 6 can be left empty
%\cventry{}{Dr. Amir Khorsandi}{Assistant Professor at Isfahan University of Technology}{}{}{khorsandi@iut.ac.ir}  % arguments 3 to 6 can be left empty

\section{Certifications}
\cvitem{TOEFL}{Score: 100 -- Date Taken: October 30, 2024}


\end{document}